---
title: "Styku Anthropomorphic Analysis"
author: "Charlotte Spencer"
date: "3/3/2021"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(ggpubr)
#install.packages("measurements")
library(measurements)

setwd("C:/Users/charlotte.spencer/OneDrive - West Point/Desktop/School/AY21-2/MA499")

```

We start by loading in our data. the data is collected into two respositories: one that includes gender information, and another that contains anthropomorphic measurements collected by the Styku Scanner.The two data tables are connected with a common key which is the cadets xnumber or cnumber.

```{r}
styku_data<-read.csv("STYKU_data.csv")
gender_xNum <- read.csv("Gender_xNumber.csv")
namesEmail <- read.csv("names and emails.csv")

namesEmail <- namesEmail%>%
  select(Full.Name, Email)%>%
  unique()

gender_xNum <- gender_xNum%>%
  select(Gender, x.Number..include.the..x..)%>%
  unique()%>%
  na.omit()

namesEmail <-full_join(namesEmail,gender_xNum, by = c("Full.Name" = "x.Number..include.the..x.."))


styku_data <- styku_data%>%
  left_join(select(namesEmail, Gender, Full.Name),by = c("Profile.Full.Name" = "Full.Name" ))%>%
  unique()

write.csv(styku_data, "styku data merged.csv")

```

## Unit Conversions

We convert inches to cm and lbs to kg
```{r}
# Height and Weight
styku_data$Weight <- conv_unit(styku_data$Weight, from = "lbs", to = "kg") # Height
styku_data$Scan.Height <- conv_unit(styku_data$Scan.Height, from = "inch", to = "cm") # Weight

# Legs
styku_data$Calf.Right <- conv_unit(styku_data$Calf.Right, from = "inch", to = "cm") # Right Calf
styku_data$Calf.Left <- conv_unit(styku_data$Calf.Left, from = "inch", to = "cm") # Left Calf

styku_data$Mid.Thigh.Right <- conv_unit(styku_data$Mid.Thigh.Right, from = "inch", to = "cm") # mid Right Thigh
styku_data$Mid.Thigh.Left <- conv_unit(styku_data$Mid.Thigh.Left, from = "inch", to = "cm") # mid Left Thigh

styku_data$Thigh.Right.Lower <- conv_unit(styku_data$Thigh.Right.Lower, from = "inch", to = "cm") # lower right thigh
styku_data$Thigh.Left.Lower <- conv_unit(styku_data$Thigh.Left.Lower, from = "inch", to = "cm") # lower left thigh

styku_data$Thigh.Right.Upper <- conv_unit(styku_data$Thigh.Right.Upper, from = "inch", to = "cm") # upper right thigh
styku_data$Thigh.Left.Upper <- conv_unit(styku_data$Thigh.Left.Upper, from = "inch", to = "cm") # upper left thigh

# Arms
styku_data$ForeArm.Right <- conv_unit(styku_data$ForeArm.Right, from = "inch", to = "cm") # right forearm
styku_data$ForeArm.Left <- conv_unit(styku_data$ForeArm.Left, from = "inch", to = "cm") # left forearm

styku_data$Bicep.Right.Lower <- conv_unit(styku_data$Bicep.Right.Lower, from = "inch", to = "cm") # right lower bicep
styku_data$Bicep.Left.Lower <- conv_unit(styku_data$Bicep.Left.Lower, from = "inch", to = "cm") # left lower bicep

styku_data$BicepRight <- conv_unit(styku_data$BicepRight, from = "inch", to = "cm") # right bicep
styku_data$Bicep.Left <- conv_unit(styku_data$Bicep.Left, from = "inch", to = "cm") # left bicep

# Torso
styku_data$Chest <- conv_unit(styku_data$Chest, from = "inch", to = "cm") # chest
styku_data$Waist..Abdominal. <- conv_unit(styku_data$Waist..Abdominal., from = "inch", to = "cm") # waist at abdominal
styku_data$Waist..Lower. <- conv_unit(styku_data$Waist..Lower., from = "inch", to = "cm") # lower waist
styku_data$Waist..Narrowest. <- conv_unit(styku_data$Waist..Narrowest., from = "inch", to = "cm") # waist at narrowest point
styku_data$Hip <- conv_unit(styku_data$Hip, from = "inch", to = "cm") # Hip
styku_data$High.Hip <- conv_unit(styku_data$High.Hip, from = "inch", to = "cm") # High Hip

```



## Correlation of Right to Left Limbs
```{r echo = T, eval = FALSE}

# For right v left forearm --> R = 0.88, p < 0.0001
cor.test(styku_data$ForeArm.Right, styku_data$ForeArm.Left, 
                    method = "pearson")
ggqqplot(styku_data$ForeArm.Right, ylab = "Right Forearm")
ggqqplot(styku_data$ForeArm.Left, ylab = "Left Forearm")
ggscatter(data= styku_data, x = "ForeArm.Right", y = "ForeArm.Left",
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          title = "Forearm: Right vs Left Correlation",
          xlab = "Right Forearm Circumference (cm)",
          ylab = "Left Forearm Circumference (cm)")

# For right v left bicep --> R = 0.89, p < 0.0001
cor.test(styku_data$BicepRight, styku_data$Bicep.Left, 
                    method = "pearson")
ggqqplot(styku_data$BicepRight, ylab = "Right Bicep")
ggqqplot(styku_data$Bicep.Left, ylab = "Left Bicep")
ggscatter(data= styku_data, x = "BicepRight", y = "Bicep.Left",
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          title = "Bicep: Right vs Left Correlation",
          xlab = "Right Bicep Circumference (cm)",
          ylab = "Left Bicep Circumference (cm)")


# For right v left lower bicep --> R = 0.91, p < 0.0001
cor.test(styku_data$Bicep.Right.Lower, styku_data$Bicep.Left.Lower, 
                    method = "pearson")
ggqqplot(styku_data$Bicep.Right.Lower, ylab = "Right Lower Bicep")
ggqqplot(styku_data$Bicep.Left.Lower, ylab = "Left Lower Bicep")
ggscatter(data= styku_data, x = "Bicep.Right.Lower", y = "Bicep.Left.Lower",
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          title = "Lower Bicep: Right vs Left Correlation",
          xlab = "Right Lower Bicep Circumference (cm)",
          ylab = "Left Lower Bicep Circumference (cm)")

# For right v left Calf --> R = 0.7, p < 0.0001
cor.test(styku_data$Calf.Right, styku_data$Calf.Left, 
                    method = "pearson")
ggqqplot(styku_data$Calf.Right, ylab = "Right Calf")
ggqqplot(styku_data$Calf.Left, ylab = "Left Calf")
ggscatter(data= styku_data, x = "Calf.Right", y = "Calf.Left",
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          title = "Calf: Right vs Left Correlation",
          xlab = "Right Calf Circumference (cm)",
          ylab = "Left Calf Circumference (cm)")

# For right v left mid thigh --> R = 0.93, p < 0.0001
cor.test(styku_data$Mid.Thigh.Right, styku_data$Mid.Thigh.Left, 
                    method = "pearson")
ggqqplot(styku_data$Mid.Thigh.Right, ylab = "Right Mid Thigh")
ggqqplot(styku_data$Mid.Thigh.Left, ylab = "Left Mid thigh")
ggscatter(data= styku_data, x = "Mid.Thigh.Right", y = "Mid.Thigh.Left",
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          title = "Mid Thigh: Right vs Left Correlation",
          xlab = "Right Mid Thigh Circumference (cm)",
          ylab = "Left id Thigh Circumference (cm)")

# For right v left lower thigh --> R = 0.95, p < 0.0001
cor.test(styku_data$Thigh.Right.Lower, styku_data$Thigh.Left.Lower, 
                    method = "pearson")
ggqqplot(styku_data$Thigh.Right.Lower, ylab = "Right Lower Thigh")
ggqqplot(styku_data$Thigh.Left.Lower, ylab = "Left Lower Thigh")
ggscatter(data= styku_data, x = "Thigh.Right.Lower", y = "Thigh.Left.Lower",
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          title = "Lower Thigh: Right vs Left Correlation",
          xlab = "Right Lower Thigh Circumference (cm)",
          ylab = "Left Lower Thigh Circumference (cm)")

# For right v left upper thigh --> R = 0.94, p < 0.0001
cor.test(styku_data$Thigh.Right.Upper, styku_data$Thigh.Left.Upper, 
                    method = "pearson")
ggqqplot(styku_data$Thigh.Right.Upper, ylab = "Right Upper Thigh")
ggqqplot(styku_data$Thigh.Left.Upper, ylab = "Left Upper Thigh")
ggscatter(data= styku_data, x = "Thigh.Right.Upper", y = "Thigh.Left.Upper",
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          title = "Upper Thigh: Right vs Left Correlation",
          xlab = "Right Upper Thigh Circumference (cm)",
          ylab = "Left Upper Thigh Circumference (cm)")

```



## Boxplots


The first plot, is a simple scatter plot showing height and weight of the participants.
```{r}
# men vs women
h_w <- styku_data%>%
  select(Profile.Full.Name, Gender, Weight, Scan.Height)%>%
  na.omit()%>%
  ggplot(aes(x = Weight, y = Scan.Height, color = Gender)) + 
  geom_point()+
  labs(title = "Height v Weight",
       y = "Height (cm)",
       x = "Weight (kg)") +
  theme(plot.title = element_text(hjust = 0.5))

h_w
# Summary Statistics for Weight
group_by(styku_data, Gender) %>%
  summarise(
    count = n(),
    mean = mean(Weight, na.rm = TRUE),
    sd = sd(Weight, na.rm = TRUE)
  )
# Summary Statistics for Height
group_by(styku_data, Gender) %>%
  summarise(
    count = n(),
    mean = mean(Scan.Height, na.rm = TRUE),
    sd = sd(Scan.Height, na.rm = TRUE)
  )

# Is weight significantly diff between men and women?
weight_W <- styku_data%>%
  select(Gender, Weight)%>% filter (Gender == "Female")
weight_M <- styku_data%>%
  select(Gender, Weight)%>% filter (Gender == "Male")
t.test(weight_W$Weight, weight_M$Weight, alternative = "two.sided", conf.level = 0.95, var.equal = FALSE)
# Yes there is a significant difference between the Weight of Men and Women

# Is height significantly diff between men and women?
height_W <- styku_data%>%
  select(Gender, Scan.Height)%>% filter (Gender == "Female")
height_M <- styku_data%>%
  select(Gender, Scan.Height)%>% filter (Gender == "Male")
t.test(height_W$Scan.Height, height_M$Scan.Height, alternative = "two.sided", conf.level = 0.95, var.equal = FALSE)
# Yes there is a significant difference in height between men and women
```


 Next we will look at Leg specific measurments.
 
```{r}
# Legs
legs <- styku_data%>%
  select(Gender, Calf.Right, Mid.Thigh.Right, Thigh.Right.Lower, Thigh.Right.Upper)%>%
  na.omit()%>%
  group_by(Gender)

calf <- ggplot(data = legs,aes(x = Gender, y = Calf.Right)) + 
  geom_boxplot() + 
  stat_summary(fun = mean, geom = "point", shape = 1, size = 3)+
  labs(title = "Calf measurments",
       y = "Single Leg Calf Circumference (cm)") + 
  theme(plot.title = element_text(hjust = 0.5))

thighs <- legs%>%
  select(Gender, Mid.Thigh.Right, Thigh.Right.Lower, Thigh.Right.Upper)%>%
  group_by(Gender)%>%
  pivot_longer(!Gender,names_to = "Region", values_to = "Circumference")%>%
  ggplot(aes(x = Gender, y = Circumference, fill = Region))+
  geom_boxplot(position = "dodge")+
  labs(title = "Thigh Circumferences",
       y = "Single Thigh Circumference (cm)")+
  theme(plot.title = element_text(hjust = 0.5))

calf
thighs

# Summary Statistics for Calves
calf_summ<-styku_data%>%
  select(Gender, Calf.Left, Calf.Right)%>%
  rowwise()%>%
  mutate(Calf = mean(c(Calf.Left,Calf.Right)))
  
calf_summ%>%
group_by(Gender) %>%
  summarise(count = n(),
    mean = mean(Calf, na.rm = TRUE),
    sd = sd(Calf, na.rm = TRUE))
# Is calf circumference significantly diff between men and women?
calf_W <- calf_summ%>%
  select(Gender, Calf)%>% filter (Gender == "Female")
calf_M <- calf_summ%>%
  select(Gender, Calf)%>% filter (Gender == "Male")
t.test(calf_W$Calf, calf_M$Calf, alternative = "two.sided", conf.level = 0.95, var.equal = FALSE)
# Yes there is a significant difference between the Calf circumference of Men and Women

# Summary Statistics for Mid Thigh
midthigh_summ<-styku_data%>%
  select(Gender, Mid.Thigh.Left, Mid.Thigh.Right)%>%
  rowwise()%>%
  mutate(MidThigh = mean(c(Mid.Thigh.Left, Mid.Thigh.Right)))
  
midthigh_summ%>%
group_by(Gender) %>%
  summarise(count = n(),
    mean = mean(MidThigh, na.rm = TRUE),
    sd = sd(MidThigh, na.rm = TRUE))
# Is mid thigh circumference significantly diff between men and women?
midthigh_W <- midthigh_summ%>%
  select(Gender, MidThigh)%>% filter (Gender == "Female")
midthigh_M <- midthigh_summ%>%
  select(Gender, MidThigh)%>% filter (Gender == "Male")
t.test(calf_W$Calf, calf_M$Calf, alternative = "two.sided", conf.level = 0.95, var.equal = FALSE)
# Yes there is a significant difference between the Mid Thigh Circumference of Men and Women

# Summary Statistics for Lower Thigh
lowerthigh_summ<-styku_data%>%
  select(Gender, Thigh.Left.Lower, Thigh.Right.Lower)%>%
  rowwise()%>%
  mutate(LowerThigh = mean(c(Thigh.Left.Lower, Thigh.Right.Lower)))
  
lowerthigh_summ%>%
group_by(Gender) %>%
  summarise(count = n(),
    mean = mean(LowerThigh, na.rm = TRUE),
    sd = sd(LowerThigh, na.rm = TRUE))
# Is lower thigh circumference significantly diff between men and women?
lowerthigh_W <- lowerthigh_summ%>%
  select(Gender, LowerThigh)%>% filter (Gender == "Female")
lowerthigh_M <- lowerthigh_summ%>%
  select(Gender, LowerThigh)%>% filter (Gender == "Male")
t.test(lowerthigh_W$LowerThigh, lowerthigh_M$LowerThigh, alternative = "two.sided", conf.level = 0.95, var.equal = FALSE)
# Yes there is a significant difference between the Lower Thigh Circumference of Men and Women

# Summary Statistics for Upper Thigh
upperthigh_summ<-styku_data%>%
  select(Gender, Thigh.Left.Upper, Thigh.Right.Upper)%>%
  rowwise()%>%
  mutate(UpperThigh = mean(c(Thigh.Left.Upper, Thigh.Right.Upper)))
  
upperthigh_summ%>%
group_by(Gender) %>%
  summarise(count = n(),
    mean = mean(UpperThigh, na.rm = TRUE),
    sd = sd(UpperThigh, na.rm = TRUE))
# Is lower thigh circumference significantly diff between men and women?
upperthigh_W <- upperthigh_summ%>%
  select(Gender, UpperThigh)%>% filter (Gender == "Female")
upperthigh_M <- upperthigh_summ%>%
  select(Gender, UpperThigh)%>% filter (Gender == "Male")
t.test(upperthigh_W$UpperThigh, upperthigh_M$UpperThigh, alternative = "two.sided", conf.level = 0.95, var.equal = FALSE)
# Yes there is a significant difference between the Lower Thigh Circumference of Men and Women
```
Next we'll compare the anthropomorphic measurements of the arms.

```{r}
#Arms
arms <- styku_data%>%
  select(Gender, ForeArm.Right, Bicep.Right.Lower, BicepRight)%>%
  na.omit()%>%
  group_by(Gender)
  
forearm <-arms%>%
  ggplot(aes(x = Gender, y = ForeArm.Right))+
  geom_boxplot()+ 
  stat_summary(fun = mean, geom = "point", shape = 1, size = 3)+
  labs(title = "Single Forearm",
       y = "Circumference (cm)") + 
  theme(plot.title = element_text(hjust = 0.5))
  
biceps <-arms%>%
  select(Gender, Bicep.Right.Lower, BicepRight)%>%
  group_by(Gender)%>%
  pivot_longer(!Gender,names_to = "Region", values_to = "Circumference")%>%
  ggplot(aes(x = Gender, y = Circumference, fill = Region))+
  geom_boxplot(position = "dodge")+
  labs(title = "Bicep Circumferences",
       y = "Circumference (cm)")+
  theme(plot.title = element_text(hjust = 0.5))

forearm
biceps

# Summary Statistics for Forearms
forearm_summ<-styku_data%>%
  select(Gender, ForeArm.Left, ForeArm.Right)%>%
  rowwise()%>%
  mutate(Forearm = mean(c(ForeArm.Right, ForeArm.Left)))
  
forearm_summ%>%
group_by(Gender) %>%
  summarise(count = n(),
    mean = mean(Forearm, na.rm = TRUE),
    sd = sd(Forearm, na.rm = TRUE))
# Is forearm circumference significantly diff between men and women?
forearm_W <- forearm_summ%>%
  select(Gender, Forearm)%>% filter (Gender == "Female")
forearm_M <- forearm_summ%>%
  select(Gender, Forearm)%>% filter (Gender == "Male")
t.test(forearm_W$Forearm, forearm_M$Forearm, alternative = "two.sided", conf.level = 0.95, var.equal = FALSE)
# Yes there is a significant difference between the Forearm Circumference of Men and Women

# Summary Statistics for Biceps
bicep_summ<-styku_data%>%
  select(Gender, Bicep.Left, BicepRight)%>%
  rowwise()%>%
  mutate(Bicep = mean(c(Bicep.Left, BicepRight)))
  
bicep_summ%>%
group_by(Gender) %>%
  summarise(count = n(),
    mean = mean(Bicep, na.rm = TRUE),
    sd = sd(Bicep, na.rm = TRUE))
# Is bicep circumference significantly diff between men and women?
bicep_W <- bicep_summ%>%
  select(Gender, Bicep)%>% filter (Gender == "Female")
bicep_M <- bicep_summ%>%
  select(Gender, Bicep)%>% filter (Gender == "Male")
t.test(bicep_W$Bicep, bicep_M$Bicep, alternative = "two.sided", conf.level = 0.95, var.equal = FALSE)
# Yes there is a significant difference between the bicep Circumference of Men and Women

# Summary Statistics for Lower Biceps
lowerbicep_summ<-styku_data%>%
  select(Gender, Bicep.Left.Lower, Bicep.Right.Lower)%>%
  rowwise()%>%
  mutate(LowerBicep = mean(c(Bicep.Left.Lower, Bicep.Right.Lower)))
  
lowerbicep_summ%>%
group_by(Gender) %>%
  summarise(count = n(),
    mean = mean(LowerBicep, na.rm = TRUE),
    sd = sd(LowerBicep, na.rm = TRUE))
# Is lower bicep circumference significantly diff between men and women?
lowerbicep_W <- lowerbicep_summ%>%
  select(Gender, LowerBicep)%>% filter (Gender == "Female")
lowerbicep_M <- lowerbicep_summ%>%
  select(Gender, LowerBicep)%>% filter (Gender == "Male")
t.test(lowerbicep_W$LowerBicep, lowerbicep_M$LowerBicep, alternative = "two.sided", conf.level = 0.95, var.equal = FALSE)
# Yes there is a significant difference between the lower bicep Circumference of Men and Women
```
Next is cmparisons of the torso.

```{r}
#Torso
torso <- styku_data%>%
  select(Gender, Chest, Waist..Abdominal., Waist..Lower., Waist..Narrowest., Hip, High.Hip)%>%
  na.omit()%>%
  group_by(Gender)

chest <- torso%>%
  ggplot(aes(x = Gender, y = Chest))+
  geom_boxplot()+ 
  stat_summary(fun = mean, geom = "point", shape = 1, size = 3)+
  labs(title = "Chest Circumference",
       y = "Circumference (cm)") + 
  theme(plot.title = element_text(hjust = 0.5))
  

waist <-torso%>%
  select(Gender, Waist..Abdominal., Waist..Lower., Waist..Narrowest.)%>%
  group_by(Gender)%>%
  pivot_longer(!Gender,names_to = "Region", values_to = "Circumference")%>%
  ggplot(aes(x = Gender, y = Circumference, fill = Region))+
  geom_boxplot(position = "dodge")+
  labs(title = "Waist Circumferences",
       y = "Circumference (cm)")+
  theme(plot.title = element_text(hjust = 0.5))

Hip <- torso%>%
  ggplot(aes(x = Gender, y = Hip))+
  geom_boxplot()+ 
  stat_summary(fun = mean, geom = "point", shape = 1, size = 3)+
  labs(title = "Hip Circumference",
       y = "Circumference (cm)") + 
  theme(plot.title = element_text(hjust = 0.5))

chest
waist

# Summary Statistics for Chest
chest_summ<-styku_data%>%
  select(Gender, Chest)%>%
  group_by(Gender) %>%
  summarise(count = n(),
    mean = mean(Chest, na.rm = TRUE),
    sd = sd(Chest, na.rm = TRUE))
# Is chest circumference significantly diff between men and women?
chest_W <- styku_data%>%
  select(Gender, Chest)%>% filter (Gender == "Female")
chest_M <- styku_data%>%
  select(Gender, Chest)%>% filter (Gender == "Male")
t.test(chest_W$Chest, chest_M$Chest, alternative = "two.sided", conf.level = 0.95, var.equal = FALSE)
# Yes there is a significant difference between the chest Circumference of Men and Women

# Summary Statistics for Waist Abdominal
wa_summ<-styku_data%>%
  select(Gender, Waist..Abdominal.)%>%
  group_by(Gender) %>%
  summarise(count = n(),
    mean = mean(Waist..Abdominal., na.rm = TRUE),
    sd = sd(Waist..Abdominal., na.rm = TRUE))
# Is Waist Abdominal circumference significantly diff between men and women?
wa_W <- styku_data%>%
  select(Gender, Waist..Abdominal.)%>% filter (Gender == "Female")
wa_M <- styku_data%>%
  select(Gender, Waist..Abdominal.)%>% filter (Gender == "Male")
t.test(wa_W$Waist..Abdominal., wa_M$Waist..Abdominal., alternative = "two.sided", conf.level = 0.95, var.equal = FALSE)
# Yes there is a significant difference between the Waist Abdominal Circumference of Men and Women

# Summary Statistics for Waist Narrowest
wn_summ<-styku_data%>%
  select(Gender, Waist..Narrowest.)%>%
  group_by(Gender) %>%
  summarise(count = n(),
    mean = mean(Waist..Narrowest., na.rm = TRUE),
    sd = sd(Waist..Narrowest., na.rm = TRUE))
# Is Waist Narrowest circumference significantly diff between men and women?
wn_W <- styku_data%>%
  select(Gender, Waist..Narrowest.)%>% filter (Gender == "Female")
wn_M <- styku_data%>%
  select(Gender, Waist..Narrowest.)%>% filter (Gender == "Male")
t.test(wn_W$Waist..Narrowest., wn_M$Waist..Narrowest., alternative = "two.sided", conf.level = 0.95, var.equal = FALSE)
# Yes there is a significant difference between the Waist Abdominal Circumference of Men and Women

# Summary Statistics for Waist Lower
wl_summ<-styku_data%>%
  select(Gender, Waist..Lower.)%>%
  group_by(Gender) %>%
  summarise(count = n(),
    mean = mean(Waist..Lower., na.rm = TRUE),
    sd = sd(Waist..Lower., na.rm = TRUE))
# Is Waist Abdominal circumference significantly diff between men and women?
wl_W <- styku_data%>%
  select(Gender, Waist..Lower.)%>% filter (Gender == "Female")
wl_M <- styku_data%>%
  select(Gender, Waist..Lower.)%>% filter (Gender == "Male")
t.test(wl_W$Waist..Lower., wl_M$Waist..Lower., alternative = "two.sided", conf.level = 0.95, var.equal = FALSE)
# No there is not a significant difference between the Lower Waist Circumference of Men and Women

# Summary Statistics for Hips
hip_summ<-styku_data%>%
  select(Gender, Hip)%>%
  group_by(Gender) %>%
  summarise(count = n(),
    mean = mean(Hip, na.rm = TRUE),
    sd = sd(Hip, na.rm = TRUE))
# Is Waist Abdominal circumference significantly diff between men and women?
hip_W <- styku_data%>%
  select(Gender, Hip)%>% filter (Gender == "Female")
hip_M <- styku_data%>%
  select(Gender, Hip)%>% filter (Gender == "Male")
t.test(hip_W$Hip, hip_M$Hip, alternative = "two.sided", conf.level = 0.95, var.equal = FALSE)
# Yes there is a significant difference between the Hip Circumference of Men and Women

# Summary Statistics for High Hips
hhip_summ<-styku_data%>%
  select(Gender, High.Hip)%>%
  group_by(Gender) %>%
  summarise(count = n(),
    mean = mean(High.Hip, na.rm = TRUE),
    sd = sd(High.Hip, na.rm = TRUE))
# Is Waist Abdominal circumference significantly diff between men and women?
hhip_W <- styku_data%>%
  select(Gender, High.Hip)%>% filter (Gender == "Female")
hhip_M <- styku_data%>%
  select(Gender, High.Hip)%>% filter (Gender == "Male")
t.test(hhip_W$High.Hip, hhip_M$High.Hip, alternative = "two.sided", conf.level = 0.95, var.equal = FALSE)
# Yes there is a significant difference between the High Hip Circumference of Men and Women
```
Finally, these BOXPLOTS are comparisons of anthropomorphic proportions. These values represent ratios of anthropomorphic measurements calculated by the Styku.

```{r}
#Proportions  
pro <- styku_data%>%
  select(Gender, Waist.Hip.Ratio..WHO., Bust.Hip.Ratio, Bust.Waist.Ratio)%>%
  na.omit()%>%
  group_by(Gender)


WaistHip <- pro%>%
  ggplot(aes(x = Gender, y = Waist.Hip.Ratio..WHO.))+
  geom_boxplot()+ 
  stat_summary(fun = mean, geom = "point", shape = 1, size = 3)+
  labs(title = "Waist v Hip ",
       y = "Ratio (Waist/Hip)") + 
  theme(plot.title = element_text(hjust = 0.5))

BustHip <- pro%>%
  ggplot(aes(x = Gender, y = Bust.Hip.Ratio))+
  geom_boxplot()+ 
  stat_summary(fun = mean, geom = "point", shape = 1, size = 3)+
  labs(title = "Bust v Hip ",
       y = "Ratio (Bust/Hip)") + 
  theme(plot.title = element_text(hjust = 0.5))

BustWaist <- pro%>%
  ggplot(aes(x = Gender, y = Bust.Waist.Ratio))+
  geom_boxplot()+ 
  stat_summary(fun = mean, geom = "point", shape = 1, size = 3)+
  labs(title = "Bust v Waist",
       y = "Ratio (Bust/Waist)") + 
  theme(plot.title = element_text(hjust = 0.5))

WaistHip
BustHip
BustWaist

```

### Cluster Analysis
```{r}
df <- styku_data%>%
  select(Bicep.Left, BicepRight, Bicep.Left.Lower, Bicep.Right.Lower,
         Bust.Hip.Ratio, Bust.Waist.Ratio,
         Calf.Left, Calf.Right, Chest,
         ForeArm.Left, ForeArm.Right,
         High.Hip, Hip, Mid.Thigh.Left, Mid.Thigh.Right,
         Thigh.Left.Lower, Thigh.Left.Upper, Thigh.Right.Lower, Thigh.Right.Upper,
         Waist..Abdominal., Waist..Lower., Waist..Narrowest.,
         Waist.Hip.Ratio..WHO., Weight, Scan.Height)%>%
  scale()
#install.packages("factoextra")
library(factoextra)
# Correlation-based distance method
res.dist <- get_dist(df, method = "pearson")
head(round(as.matrix(res.dist), 2))[, 1:6]
# Visualize the dissimilarity matrix
fviz_dist(res.dist, lab_size = 8)

# Enhanced k-means clustering
res.km <- eclust(df, "kmeans", nstart = 25)
# Gap statistic plot
fviz_gap_stat(res.km$gap_stat)
# Silhouette plot
fviz_silhouette(res.km)
# Optimal number of clusters using gap statistics
res.km$nbclust
# Print result
 res.km
 
# Enhanced hierarchical clustering
res.hc <- eclust(df, "hclust") # compute hclust
fviz_dend(res.hc, rect = TRUE) # dendrogam
fviz_silhouette(res.hc) # silhouette plot
fviz_cluster(res.hc) # scatter plot


```


